|

### 2023-05-10 paper/00-main.Rmd
figure captions and more

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  cache = TRUE
)
library(here)
```

>>>>

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.pos = "p",
  cache = TRUE
)
library(here)
```

### 2023-05-10 paper/01-introduction.Rmd
figure captions and more

Table \ref{tab:metrics} gives a summary of existing pass-rush metrics.

Officially tracked by the NFL since 1982, the most well-known statistic for evaluating defensive linemen on pass rushing plays is the sack, which occurs when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.  Sacks represent a simple binary measure of success for a rusher on a pass play.  However, there are many intermediate outcomes for a rusher that can also be considered successes that don't result in a sack.  Measures such a hits and hurries are collected by various outlets where hits counts the number of times a QB is hit while passing and hurries counts how often a QB has to throw the ball earlier than they would have liked to.

@@

[Pro football ref has a slightly different QB pressures formula than the formula below https://www.pro-football-reference.com/about/advanced_stats.htm]

@@

All the aforementioned methods suffered from not having the data that was actually necessary to develop a meaningful metric for linemen in football, either offensive or defensive.  Now though, thanks to the 2023 Big Data Bowl, we have a publicly available tracking data not only for the linemen, but for every player on the field!  With this data performance of offensive and defensive linemen can be meaningfully assessed, though we focus solely on the performance of defensive linemen here.  This manuscript presents a metric we refer to as STRAIN based on a concept of the same name from materials science.  STRAIN gives a continuous measure of pressure for each of the defensive linemen over the course of an entire play allowing for the measurement of the level of success of the pass rush even on plays that don't result in an easily observed outcome like a sack, hit, or hurry.  We view this as a major step forward in the accurate evaluation of defensive linemen performance.  Further, we note than while we focus exclusively on defensive linemen here, the proposed metric STRAIN is relatively easily extended to the evaluation of offensive linemen performance.

The remainder of this paper is outlined as follows. Section \ref{sec:data} describes the data set from the 2023 Big Data Bowl.  Section \ref{sec:methods} introduces the formal definition of STRAIN.  Section \ref{sec:results} studies the performance of the proposed metric.  We end with Section \ref{sec:discussion} where we present a discussion of future directions for STRAIN.

>>>>

Table \ref{tab:metrics} gives a summary of existing pass-rush metrics.
We now highlight what these quantities measure as well as their limitations.

Officially tracked by the NFL since 1982, the most well-known statistic for evaluating defensive linemen on pass rushing plays is the sack.
A sack is recorded when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.
Sacks represent a simple binary measure of success for a rusher on a pass play.
However, there are many intermediate outcomes for a rusher that can also be considered successes that do not result in a sack.
Measures such a hits and hurries are collected by various outlets where hits counts the number of times a QB is hit while passing and hurries counts how often a QB has to throw the ball earlier than they would have liked to.

@@

<!-- [Pro football ref has a slightly different QB pressures formula than the formula below https://www.pro-football-reference.com/about/advanced_stats.htm] -->

@@

All the aforementioned methods suffered from not having the data that was actually necessary to develop a meaningful metric for linemen in football, either offensive or defensive.
Now though, thanks to the 2023 Big Data Bowl, we have a publicly available tracking data not only for the linemen, but for every player on the field.
This allows us to meaningfully assess the performance of linemen in football.
In this paper, we focus on defensive linemen, and propose STRAIN, a metric for pass rush evaluation inspired by the concept of strain rate in materials science.
STRAIN gives a continuous measure of pressure for each of the defensive linemen over the course of an entire play.
This allows for the measurement of pass rush success even on plays that do not result in an observed outcome like a sack, hit, or hurry.
We view this as a major step forward in the accurate evaluation of defensive linemen performance.
Further, we note than while we focus exclusively on defensive linemen here, the proposed metric STRAIN is relatively easily extended to the evaluation of offensive linemen performance.

The remainder of this paper is outlined as follows.
We first describe the player tracking data provided by 2023 Big Data Bowl in Section \ref{sec:data}.
We then introduces the formal definition of our metric STRAIN and our modeling approach in Section \ref{sec:methods}.
We present an real-game illustration of the proposed metric and study its performance in Section \ref{sec:results}.
We close with a discussion of future directions for STRAIN in Section \ref{sec:discussion}.

### 2023-05-10 paper/02-data.Rmd
figures + tables formatting
figure captions and more

\begin{table}
\caption{Example of tracking data for a play during the Las Vegas Raiders versus Denver Broncos NFL game on October 17, 2021. The data shown here is for Raiders DE Maxx Crosby, and the frames included are between the ball snap and when the sack by Crosby is recorded. \label{tab:track}}
\centering
\begin{tabular}{ccccccccccc}
\hline
frameId & jerseyNumber & team & x & y & s & a & dis & o & dir & event \\ 
\hline
7 & 98 & LV & 67.68 & 29.89 & 0.34 & 1.57 & 0.04 & 124.86 & 88.21 & ball\_snap \\ 
8 & 98 & LV & 67.76 & 29.89 & 0.69 & 2.13 & 0.08 & 124.07 & 89.59 & None \\ 
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots \\ 
50 & 98 & LV & 73.67 & 25.06 & 4.19 & 2.62 & 0.42 & 134.21 & 125.26 & qb\_sack \\ 
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Example of tracking data for a play during the Las Vegas Raiders versus Denver Broncos NFL game on October 17, 2021. The data shown here are for Raiders DE Maxx Crosby, and the frames included are between the ball snap and when the sack by Crosby is recorded. \label{tab:track}}
\centering
\begin{tabular}{ccccccccc}
\hline
frameId & x & y & s & a & dis & o & dir & event \\ 
\hline
7 & 67.68 & 29.89 & 0.34 & 1.57 & 0.04 & 124.86 & 88.21 & ball\_snap \\ 
8 & 67.76 & 29.89 & 0.69 & 2.13 & 0.08 & 124.07 & 89.59 & None \\ 
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots \\ 
50 & 73.67 & 25.06 & 4.19 & 2.62 & 0.42 & 134.21 & 125.26 & qb\_sack \\ 
\hline
\end{tabular}
\end{table}

### 2023-05-10 paper/03-methods.Rmd
more results writing
figure captions and more

Moreover, since we observe STRAIN continuously at every tenth of a second within each play, we can then compute the average STRAIN across all frames played for every pass rusher.
This can be helpful in regards to player evaluation, as we can determine the most effective pass-rushers based on their average STRAIN values.
Formally, the average STRAIN, denoted by $\overline{\text{STRAIN}}$, for pass rusher $i$ over $n$ total plays with $T$ total frames is

[CHECK THIS - is notation consistent with what we have above?]
\begin{equation}
\overline{\text{STRAIN}}_{i} = \frac{1}{n} \sum_{t=1}^T {\text{STRAIN}}_{i}(t).
\end{equation}

@@

To this end, we fit a multilevel model to evaluate pass rushers' impact on the average STRAIN observed in a play, while accounting for their pass blocker, QB, and play-level information.
We identify the pass blocker linked with the pass rusher of interest using the data provided by PFF.
Since there can be multiple blockers linked to a rusher, for simplicity we only consider the nearest blocker positioned to the pass rusher at the start of the play.
We use random intercepts for the three player groups: (1) pass rushers as $R$, (2) nearest pass blockers as $B$, and (3) QBs as $Q$.
The coefficients $\beta$ for additional information $X_{j,i}$ about pass rusher $j$ in play $i$ are estimated as fixed-effects. 
Our model for the average STRAIN by pass rusher $j$ on play $i$ is as follows.
\begin{equation}
\begin{aligned}
\overline{\text{STRAIN}}_{j,i} &\sim N(R_{r[j,i]} + B_{b[j,i]} + Q_{q[i]} + X_{j,i} \cdot \beta, \sigma^2), \text{ for } i = 1, \dots, n \text{ plays} \\
R_{r} &\sim N(\mu_R, \sigma^2_R), \text{ for } r = 1, \cdots, \text{ \# of pass rushers}, \\
B_{b} &\sim N(\mu_B, \sigma^2_B), \text{ for } b = 1, \cdots, \text{ \# of pass blockers}, \\
Q_{q} &\sim N(\mu_Q, \sigma^2_Q), \text{ for } q = 1, \cdots, \text{ \# of QBs}.
\end{aligned}
\end{equation}

We consider a normal distribution to obtain the random intercepts for each player toward their respective position group means.
This provides us with average individual effects on STRAIN for each player while applying shrinkage, which is a useful property in this problem's context since we do not observe the same number of plays for each player.
With regards to the fixed-effects about pass rusher $j$ in play $i$, we include the length of the play, the pass rusher position, the nearest pass blocker's position, and the number of pass blockers assigned to the pass rusher based on the PFF data.
Table \ref{tab:pos} shows our categorization of position for the pass rush and pass block roles.
We implement the model using penalized likelihood via the `lme4` package in `R` [@bateslme4; @R2023Language].

\begin{table}
\caption{Position groupings for pass rushers and blockers. \label{tab:pos}}
\centering
\begin{tabular}{ll}
\hline
Role & Position \\ 
\hline
Pass rush & Defensive end \\ 
Pass rush & Defensive tackle \\ 
Pass rush & Nose tackle \\ 
Pass rush & Outside linebacker \\ 
Pass rush & Interior linebacker (middle and inside linebackers) \\ 
Pass rush & Secondary (cornerback, free safety, and strong safety) \\
\hline
Pass block & Center \\ 
Pass block & Guard \\ 
Pass block & Tackle \\ 
Pass block & Other (tight end, running back, fullback, wide receiver) \\ 
\hline
\end{tabular}
\end{table}

>>>>

Moreover, since we observe STRAIN continuously at every tenth of a second within each play, we can then compute the average STRAIN across all frames played for every pass rusher.
Formally, the average STRAIN, denoted by $\overline{\text{STRAIN}}$, for pass rusher $i$ over $n$ total plays with $T$ total frames is
[CHECK THIS - is notation consistent with what we have above?]
\begin{equation}
\overline{\text{STRAIN}}_{i} = \frac{1}{n} \sum_{t=1}^T {\text{STRAIN}}_{it}.
\end{equation}
This can be helpful for player evaluation, as we determine the most effective pass-rushers based on their average STRAIN values in Section \ref{sec:strainbar}.
We also use average STRAIN to assess statistical properties of our metric in Section \ref{sec:statprop}.

@@

To this end, we fit a multilevel model to evaluate pass rushers' impact on the average STRAIN observed in a play, while accounting for their pass blocker, QB, and play-level information.
We identify the pass blocker linked with the pass rusher of interest using the data provided by PFF.
Since there can be multiple blockers linked to a rusher, for simplicity we only consider the nearest blocker positioned to the pass rusher at the start of the play.
We use random intercepts for the three player groups: (1) pass rushers as $R$, (2) nearest pass blockers as $B$, and (3) QBs as $Q$.
The coefficients $\beta$ for additional information $X_{j,i}$ about pass rusher $j$ in play $i$ are estimated as fixed-effects. 
Our model for the average STRAIN by pass rusher $j$ on play $i$ is as follows.
\begin{equation}
\begin{aligned}
\overline{\text{STRAIN}}_{ij} &\sim N(R_{r[ij]} + B_{b[ij]} + Q_{q[i]} + X_{ij} \cdot \beta, \sigma^2), \text{ for } i = 1, \dots, n \text{ plays} \\
R_{r} &\sim N(\mu_R, \sigma^2_R), \text{ for } r = 1, \cdots, \text{ \# of pass rushers}, \\
B_{b} &\sim N(\mu_B, \sigma^2_B), \text{ for } b = 1, \cdots, \text{ \# of pass blockers}, \\
Q_{q} &\sim N(\mu_Q, \sigma^2_Q), \text{ for } q = 1, \cdots, \text{ \# of QBs}.
\end{aligned}
\end{equation}

We consider a normal distribution to obtain the random intercepts for each player toward their respective position group means.
This provides us with average individual effects on STRAIN for each player while applying shrinkage, which is a useful property in this problem's context since we do not observe the same number of plays for each player.
With regards to the fixed-effects about pass rusher $j$ in play $i$, we include the length of the play, the pass rusher position, the nearest pass blocker's position, and the number of pass blockers assigned to the pass rusher based on the PFF data.
Table \ref{tab:pos} shows our positional categorization for the pass rush and pass block roles.
We implement the model using penalized likelihood via the `lme4` package in `R` [@bateslme4; @R2023Language].

\begin{table}
\caption{Position groupings for pass rushers and blockers. \label{tab:pos}}
\centering
\begin{tabular}{ll}
\hline
Role & Position \\ 
\hline
Pass rush & Defensive end \\ 
Pass rush & Defensive tackle \\ 
Pass rush & Nose tackle \\ 
Pass rush & Outside linebacker \\ 
Pass rush & Interior linebacker (middle linebacker, inside linebacker) \\ 
Pass rush & Secondary (cornerback, free safety, strong safety) \\
\hline
Pass block & Center \\ 
Pass block & Guard \\ 
Pass block & Tackle \\ 
Pass block & Other (tight end, running back, fullback, wide receiver) \\ 
\hline
\end{tabular}
\end{table}

### 2023-05-10 paper/04-results.Rmd
figure captions and more

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

Moreover, Figure \ref{fig:fig_crosby_curves} clearly demonstrates the interactions between the features for Maxx Crosby.
Here, a higher STRAIN generally corresponds to faster moving rate towards the quarterback.
STRAIN also increases as the distance between the pass rusher and quarterback is being reduced.
Both of these relationships suggest an overall successful pass rush by Maxx Crosby.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "strain curve for unsuccessful play"
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those. 
It is striking that for plays with sack outcome,

## Ranking the best pass-rushers

@@

## Statistical Properties of STRAIN

@@

some sentences

Next, we examine the predictability of STRAIN as a measure of pressure.
We first look at how well strain correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} is a scatterplot of average STRAIN and pressure rate which reveals a fairly strong correlation (r = 0.625) between the quantities.
Note that we only consider players with at least 100 snaps played.
Furthermore, the average STRAIN for the first 4 weeks of the 2021 season is more predictive of the last 4 weeks' pressure rate ($r=0.322$) than the first 4 weeks' pressure rate ($r=0.097$), as illustrated in Figure \ref{fig:fig_predictability}.

We also examine the stability of STRAIN over time by comparing the average STRAIN across all frames played in first and last four weeks of the 2021 NFL regular season.
It is apparent from Figure \ref{fig:fig_stability} that there is a strong correlation $(r = 0.854)$ for this relationship, illustrating that STRAIN is a stable quantity over the provided 8-week window.

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between  with pressure rate = (hits + sacks + hurries) per snap"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

```{r}
#| label: fig_predictability
#| fig.cap: "strain is more predictive of pressure rate than pressure rate itself."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```

```{r}
#| label: fig_stability
#| fig.cap: "Metric stability"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

There are a variety of quantities we're interested in from the multilevel model fit in Section \ref{sec:methods}.
First, Table \ref{tab:fixedeff} displays the results for the fixed effects terms.
[INSERT CONCLUSIONS ABOUT THESE VARIABLES]
Next, Table \ref{tab:icc} displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker.
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

\begin{table}
\caption{Fixed effects for the multilevel model. \label{tab:fixedeff}}
\centering
\begin{tabular}{rrrrrr}
  \hline
 & estimate & se & df & $t$-statistic & $p$-value \\ 
  \hline
Intercept & 0.355 & 0.010 & 332.288 & 35.688 & 0.000 \\ 
  play\_len & -0.004 & 0.000 & 30653.793 & -38.214 & 0.000 \\ 
  rush\_posDT & -0.081 & 0.008 & 369.713 & -10.340 & 0.000 \\ 
  rush\_posinteriorLB & 0.058 & 0.011 & 770.441 & 5.332 & 0.000 \\ 
  rush\_posNT & -0.106 & 0.012 & 355.999 & -9.173 & 0.000 \\ 
  rush\_posOLB & 0.062 & 0.008 & 388.506 & 7.695 & 0.000 \\ 
  rush\_possecondary & 0.145 & 0.012 & 1734.779 & 12.328 & 0.000 \\ 
  block\_posG & 0.011 & 0.006 & 123.672 & 1.867 & 0.064 \\ 
  block\_posother & 0.010 & 0.008 & 500.451 & 1.261 & 0.208 \\ 
  block\_posT & 0.023 & 0.006 & 161.556 & 3.625 & 0.000 \\ 
  n\_blockers & -0.064 & 0.003 & 30949.514 & -24.788 & 0.000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{ICC. \label{tab:icc}}
\centering
\begin{tabular}{rlr}
\hline
Group & ICC \\ 
\hline
nflId & 0.057 \\ 
blocker\_id & 0.012 \\ 
passer & 0.023 \\ 
residual & 0.907 \\ 
\hline
\end{tabular}
\end{table}

@@

```{r}
#| label: fig_rankings_boot
#| fig.cap: "steve"
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```

>>>>

```{r}
#| label: fig_crosby_curves
#| fig.cap: "The change in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a unsuccessful pass rush play that results in a sack."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

Moreover, Figure \ref{fig:fig_crosby_curves} clearly demonstrates the interactions between the features for Maxx Crosby.
Here, a higher STRAIN generally corresponds to faster moving rate towards the quarterback.
STRAIN also increases as the distance between the pass rusher and quarterback is being reduced.
Both of these relationships suggest an overall successful pass rush by Maxx Crosby.
It is also notable that Crosby, who is credited with a sack, generates more STRAIN than other pass rushers during this play.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "The change in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of an unsuccessful pass rush play."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those. 
We clearly see that players tend to generate more STRAIN when a play ends in a hit, sack, or hurry, compared to no outcome.
Within the three pressure metrics, it is not surprised that a sack corresponds to the highest amount of STRAIN.
[Can we say anything about why NT has highest curve when there's a sack?]

## Ranking the best pass-rushers {#sec:strainbar}

@@

## Statistical Properties of STRAIN {#sec:statprop}

@@

Next, we examine different statistical properties of our proposed metric STRAIN.
Our focus here is to understand the stability and predictability of STRAIN, and we pose the following question:
How much does our metric vary from week to week?
In other words, is previous performance predictive of future performance based on our metric?
Below, we attempt the answer these questions, and the following results are for pass rushers with at least 100 snaps played during the first 8 weeks of the 2021 NFL regular season.

We first investigate the predictability of STRAIN as a measure of pressure.
In particular, we look at how well our metric correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} is a scatterplot of average STRAIN and pressure rate over the course the provided 8-game sample, which reveals a fairly strong correlation ($r =0.625$) between the quantities.
Furthermore, the average STRAIN for the first 4 weeks of the 2021 season is more predictive of the last 4 weeks' pressure rate ($r=0.322$) than the first 4 weeks' pressure rate ($r=0.097$), as illustrated in Figure \ref{fig:fig_predictability}.
We also analyze the stability of STRAIN over time by comparing the average STRAIN across all frames played in first and last four weeks of the 2021 NFL regular season.
It is apparent from Figure \ref{fig:fig_stability} that there is a strong correlation $(r = 0.854)$ for this relationship, illustrating that STRAIN is a stable quantity over the provided 8-week window.

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between average STRAIN and pressure rate (total hits, sacks, and hurries per snap) over the first 8 weeks of the 2021 NFL season. There is a moderately strong association between average STRAIN and pressure rate ($r =0.625$). Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

```{r}
#| label: fig_predictability
#| fig.cap: "Relationships between pressure rate for the last 4 weeks of the 2021 NFL season and first 4 weeks' pressure rate (left) and average STRAIN (right). STRAIN is more predictive ($r=0.322$) of future pressure rate than previous pressure rate itself ($r=0.097$). Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```

```{r}
#| label: fig_stability
#| fig.cap: "Relationships between average STRAIN for the last and first 4 weeks of the 2021 NFL season. A strong linear correlation ($r = 0.854$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

There are a variety of quantities we are interested in from the multilevel model fit mentioned in Section \ref{sec:methods}.
First, Table \ref{tab:fixedeff} displays the results for the fixed effects terms.
[INSERT CONCLUSIONS ABOUT THESE VARIABLES]
Next, Table \ref{tab:icc} displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker.
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

\begin{table}
\caption{Fixed-effects coefficients estimates for the multilevel model. \label{tab:fixedeff}}
\centering
\begin{tabular}{rrrrrr}
  \hline
 & estimate & se & df & $t$-statistic & $p$-value \\ 
  \hline
Intercept & 0.355 & 0.010 & 332.288 & 35.688 & 0.000 \\ 
  play\_len & -0.004 & 0.000 & 30653.793 & -38.214 & 0.000 \\ 
  rush\_posDT & -0.081 & 0.008 & 369.713 & -10.340 & 0.000 \\ 
  rush\_posinteriorLB & 0.058 & 0.011 & 770.441 & 5.332 & 0.000 \\ 
  rush\_posNT & -0.106 & 0.012 & 355.999 & -9.173 & 0.000 \\ 
  rush\_posOLB & 0.062 & 0.008 & 388.506 & 7.695 & 0.000 \\ 
  rush\_possecondary & 0.145 & 0.012 & 1734.779 & 12.328 & 0.000 \\ 
  block\_posG & 0.011 & 0.006 & 123.672 & 1.867 & 0.064 \\ 
  block\_posother & 0.010 & 0.008 & 500.451 & 1.261 & 0.208 \\ 
  block\_posT & 0.023 & 0.006 & 161.556 & 3.625 & 0.000 \\ 
  n\_blockers & -0.064 & 0.003 & 30949.514 & -24.788 & 0.000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{ICC. \label{tab:icc}}
\centering
\begin{tabular}{rlr}
\hline
Group & ICC \\ 
\hline
Pass rusher & 0.057 \\ 
Pass blocker & 0.012 \\ 
Quarterback & 0.023 \\ 
Residual & 0.907 \\ 
\hline
\end{tabular}
\end{table}

@@

```{r}
#| label: fig_rankings_boot
#| fig.cap: "Top 10 pass rushers for each position (DE, DT, NT, OLB) by mean varying intercept."
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```
